Target Markdown

### 2024-02-22 _targets.Rmd

>>>>

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = tibble::tibble(
  names = c("no_rerun", "non_allo_no_rerun", "rerun")
    ),
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    }
  ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

```{r, eval = FALSE}
tar_load(c(sem_simplified_eff_tab_no_rerun, sem_simplified_eff_tab_rerun,
    sem_simplified_eff_tab_non_allo_no_rerun))
sem_simplified_eff_tab_no_rerun %>%
  filter(effect_type == "total", response %in% c("pop_stab"))
sem_simplified_eff_tab_rerun %>%
  filter(effect_type == "total", response %in% c("pop_stab"))
sem_simplified_eff_tab_non_allo_no_rerun %>%
  filter(effect_type == "total", response %in% c("pop_stab"))
```

```{r, eval = FALSE}
library(tidyverse)
library(magrittr)
tar_load(c(sim_fw_no_rerun, sim_fw_rerun))
sim_id <- intersect(sim_fw_no_rerun$sim_id, sim_fw_rerun$sim_id)
cor(
  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$stab_com, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$stab_com, use = "pairwise.complete.obs"
)
cor(
  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$richness, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$richness, use = "pairwise.complete.obs"
)
cor(
  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$async, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$async, use = "pairwise.complete.obs"
)
cor(
  sim_fw_no_rerun[sim_fw_no_rerun$sim_id %in% sim_id, ]$stab_pop, sim_fw_rerun[sim_fw_rerun$sim_id %in% sim_id, ]$stab_pop, use = "pairwise.complete.obs"
)
```
